\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

\medskip
 Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}. During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with long elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'. In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface. The interface becomes unstable and collapses, taking a curved shape. In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX. The higher the velocity of the injected fluid, the less wide (tip-splitting behaviour) the finger will be. In addition, pressure differences %(eq.\ref{eq:pressure_dif}) 
acting on the interface will produce a net pressure force,

>>>>

\medskip
 Under the assumption that fluids remain immiscible along an interface, surface tension plays an important role in determining the shape and progress of the fingers~\citep{howison_2000}. During the displacement of a fluid by a less viscous one, the expected uniform front is perturbed \citep[described by the Buckley-Leverett theory of immiscible displacement][]{sheldon_1959} leading to an uneven front with elongations of the outside edge of the fluid interface (Fig.~\ref{fig:simple_case}), often referred as 'fingers'. In homogeneous domains, fingers start to develop when the surface tension acting on the interface between the fluids exert an opposite force towards the change of shape of the interface. The interface becomes unstable and collapses, taking a curved shape.

In heterogeneous domains, such instability may also be triggered by permeability differences between smaller regions as is shown in Section XXX. The higher the velocity of the low viscosity fluid, the less wide (tip-splitting behaviour) the finger will be. In addition, pressure differences %(eq.\ref{eq:pressure_dif}) 
acting on the interface will produce a net pressure force,
